Visualizing probability distributions across bivariate cyclic temporal granularities

### 2020-08-05 main.Rmd
shifting code to script folder

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(bookdown)
library(rticles)
library(knitr)
library(tidyverse)
library(lubridate)
library(lvplot)
library(ggridges)
library(tsibble)
if (requireNamespace("gravitas") == F)
  remotes::install_github("Sayani07/gravitas")
library(gravitas)
library(ggpubr)
library(xtable)
library(kableExtra)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
#knitr::opts_knit$set(root.dir = here::here())
```

```{r external, include = FALSE}
# read_chunk('scripts/main.R')
```

@@

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="Illustration of time domain, linear granularities and index set.  Hour, day, week, month and year are linear granularities and can also be considered to be time domains. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating. Hours could also be considered the index set, and a bottom granularity. "}
knitr::include_graphics("Figs/linear-ex.png")
```

@@

```{r circular-dow,echo=FALSE,out.width = "100%",fig.cap="Illustration of circular relative to linear granularities (a). Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b). The circular granularity creates repeated integer sequences."}
knitr::include_graphics("Figs/circular-ex.png")
```

@@

```{r search, echo=FALSE, eval = FALSE}
library(gravitas)
smart_meter %>%
  search_gran(filter_out = c("semester", 
                             "quarter",
                             "fortnight"))
```

@@

```{r hierarchy-cric}
library(gravitas)
library(tibble)
hierarchy_model <- tibble::tibble(
  `linear (G)` = c("over", "inning", "match", "season"),
  `single-order-up cyclic (C)` = c("over-of-inning", "inning-of-match", "match-of-season", 1),
  `period length/conversion operator (K)` = c(20, 2, "k(match, season)", 1)
)
knitr::kable(hierarchy_model,
             format = "latex",
             booktabs = TRUE,
             caption = "Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.") %>%
  #row_spec(0, bold = TRUE)%>%
  kable_styling()
```

@@

library(tsibble)

@@

<!--The infrastructure of systematic exploration of observed variable across pair of cyclic time granularities has been implemented in the
R package `gravitas`. --> A missing piece is to enable user-defined temporal calendars. Also, computation of cyclic aperiodic granularities would require computing aperiodic linear granularities first. A few R packages like `almanac` and `gs` provide functionality to create recurring events that are not periodic. These functions can be imported in the `gravitas` package to accommodate for aperiodic cyclic granularities. Another future direction of work could be to further refine the search of harmonies by only selecting pairs of cyclic granularities for which variation in measured variable is significant and rating these selected harmony pairs in order of importance for exploration.

>>>>

```{r initial, echo = FALSE, cache = FALSE, include = FALSE}
options("knitr.graphics.auto_pdf" = TRUE)
library(knitr)
opts_chunk$set(
  echo = FALSE, warning = FALSE, message = FALSE, comment = "#>",
  fig.path = "figure/", fig.align = "center", fig.show = "hold",
  cache = TRUE, cache.path = "cache/",
  out.width = ifelse(is_html_output(), "100%", "\\textwidth")
)
#knitr::opts_knit$set(root.dir = here::here())
```

```{r external, include = FALSE, cache = FALSE}
read_chunk('scripts/main.R')
```

@@

```{r linear-time, echo=FALSE, out.width = "100%", fig.cap="Illustration of time domain, linear granularities and index set.  Hour, day, week, month and year are linear granularities and can also be considered to be time domains. These are ordered with ordering guided by integers and hence is unidirectional and non-repeating. Hours could also be considered the index set, and a bottom granularity. "}
```

@@

```{r circular-dow,echo=FALSE,out.width = "100%",fig.cap="Illustration of circular relative to linear granularities (a). Circular granularities can be considered to be cutting the linear granularity into pieces and stacking them (b). The circular granularity creates repeated integer sequences."}

@@

```{r search, echo=FALSE, eval = FALSE}
smart_meter %>%
  search_gran(filter_out = c("semester", 
                             "quarter",
                             "fortnight"))
```

@@

```{r hierarchy-cric}
hierarchy_model <- tibble::tibble(
  `linear (G)` = c("over", "inning", "match", "season"),
  `single-order-up cyclic (C)` = c("over-of-inning", "inning-of-match", "match-of-season", 1),
  `period length/conversion operator (K)` = c(20, 2, "k(match, season)", 1)
)
knitr::kable(hierarchy_model,
             format = "latex",
             booktabs = TRUE,
             caption = "Hierarchy table for cricket where overs are nested within an inning, innings nested within a match and matches within a season.") %>%
  #row_spec(0, bold = TRUE)%>%
  kable_styling()
```

@@

@@

<!--The infrastructure of systematic exploration of observed variable across pair of cyclic time granularities has been implemented in the
R package `gravitas`. --> A missing piece in the package `gravitas` is the  computation of cyclic aperiodic granularities which would require computing aperiodic linear granularities first. A few R packages like `almanac` and `gs` provide functionality to create recurring events that are not periodic. These functions can be imported in the `gravitas` package to accommodate for aperiodic cyclic granularities. Another future direction of work could be to further refine the search of harmonies by only selecting pairs of cyclic granularities for which variation in measured variable is significant and rating these selected harmony pairs in order of importance for exploration.
